---
title: "Geomophological units"
author: "VCL"
date: "August 29, 2018"
output: html_document:
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Teste 

Parâmetros do terreno  SAGA V.2.2.3

```{r, warning=FALSE}
#setwd("c:/geom")
list.files (pattern = '^.*\\.asc$') #listando todos os arquivos .asc
```

```{r, warning=FALSE}


TP.list <- list.files(getwd(), pattern= '^.*\\.asc$', full.names = TRUE) #arquivos de extens?o asc
TP.list <- TP.list [-9]     #Retirando o Flow Direction
TP.list

```




```{r}
grids5m <- raster::stack(TP.list)
class(grids5m)
summary (grids5m)


```

## **Resumo dos dados**


Parâmetros SAGA:

Dataset               | Descrição                        |  Método                          | Unidade
----------------------|----------------------------------|----------------------------------|---------
"aspect.asc"          | Aspecto                          | Evans, 1979 (2nd order polynom)  | Radians
"baselev.asc"         | Elevaçãoo do nível de base       | ta_channels SAGA V2.2.3^*^       | m
"c_area.asc"          | Área de contribuição  dwonslope  | Freeman 1994 (multiple direction)| m^2^               
"c_long.asc"          | Curvatura longitudinal           | Evans, 1979 (2nd order polynom)  | Normalized
"c_tan.asc"           | Curvatura Tangencial             | Evans, 1979 (2nd order polynom)  | Normalized          
"dem.asc"             | Modelo digital de elevação       | Hutchinson, 1996 (ANUDEM)        | m
"slope.asc"           | Declividade                      | Evans 1979 (2nd order polynom)   | Radians
"grad_downslp.asc"    | Gradient downslope distance      | Hjerdt et.al, 2004               | degree
"grad_downslp_dif.asc"| (grad_downslp.asc - slope.asc)   | Hjerdt et.al, 2004               | degree
"hofd.asc"            | Horizontal overland flow distance| Nobre, 2011 (Nearest Drainage)   | m 
"ofdcn.asc"           | Overland flow distance to channel| Nobre, 2011 (Nearest Drainage)   | m
"vdcn.asc"            | Vertical distance to channel     | ta_channels SAGA V2.2.3^*^       | m
"vofd.asc"            | Vertical overland flow distance  | Nobre, 2011 (Nearest Drainage)   | m


**^*^**: This module calculates the vertical distance to a channel network base level. The algorithm consists of two major steps: 1. Interpolation of a channel network base level elevation 2. Subtraction of this base level from the original elevations. Author: O.Conrad (c) 2002


```{r,eval= TRUE, echo= FALSE, message=FALSE, warning=FALSE}
#### # Filtrando Data set 

hist.grids <- raster::stack(grids5m[[- c(3,4,5,6)]])
log.grids <-  raster::stack(grids5m[[c(3,4,5,6)]])# Exibir em base logarítima
```


```{r,eval= TRUE, echo= FALSE, message=FALSE, warning=FALSE}
#### Histogramas 
library(raster)

hist(hist.grids, breaks=25, col="grey25", na.rm=TRUE)
#hist(log.grids, breaks=25, col="grey25")

```

```{r,eval= TRUE, echo= FALSE, message=FALSE, warning=FALSE}
#### Base log 
hist(log(log.grids), breaks=25, col="grey25")

```


## Including Plots

Plot Raster object:

```{r}

plot(grids5m[[9]], main ="Gradient Doownslope difference ")



```


